Figures

### 2019-04-26 figures/07_model-selection.Rmd
model exploration

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r 02_hierarchical_demo, echo=FALSE, message=TRUE, eval=TRUE}
# setwd("figures")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
                summarize(
                  group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
                           lagoslakeid), 
                  tp = median(tp, na.rm = TRUE), 
                  chla = median(chla, na.rm = TRUE)), 
                by = "lagoslakeid") %>%
  tidyr::drop_na()

dt <- dplyr::select(readRDS("../data/dt.rds"), "lagoslakeid") %>% 
  left_join(ep, by = "lagoslakeid")

@@

# join iws ag
dt <- left_join(dt, ungroup(dplyr::select(mutate(
  group_by(lg$iws.lulc, lagoslakeid), 
  ag_pct = sum(iws_nlcd2011_pct_81,
                           iws_nlcd2011_pct_82, na.rm = TRUE)), 
  lagoslakeid, ag_pct))
  )

@@

cowplot::plot_grid(
  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
  ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat)) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
    theme_minimal() +
    theme(legend.position = "bottom",
          axis.title = element_blank(),
          legend.title = element_blank()) +
    scale_fill_manual(values = colors, levels(hu4$n_cat)),
  rel_heights = c(0.6, 1), labels = "AUTO"
)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r ```{r 07_model_selection, fig.height=3, echo=FALSE}

# setwd("figures")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

# ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
#                 summarize(
#                   group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
#                            lagoslakeid), 
#                   tp = median(tp, na.rm = TRUE), 
#                   chla = median(chla, na.rm = TRUE)), 
#                 by = "lagoslakeid") %>%
#   tidyr::drop_na()

dt <- readRDS("../data/dt.rds") %>%
  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", "ag_pct", "phosphorus_fertilizer_use")

@@

# join iws ag
# dt <- left_join(dt, ungroup(dplyr::select(mutate(
#   group_by(lg$iws.lulc, lagoslakeid), 
#   ag_pct = sum(iws_nlcd2011_pct_81,
#                            iws_nlcd2011_pct_82, na.rm = TRUE)), 
#   lagoslakeid, ag_pct))
#   )

@@

plot_grid(
  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
  ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat)) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)), 
  rel_heights = c(0.6, 1), labels = "AUTO"
)
```

```{r brms_stan}
library(brms)

names(dt) <- gsub("_", "v", names(dt))

# linear
model_form <- bf(tp ~ agvpct)

# linear re
model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))

# non-linear re
model_form <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + 
                   (1|hu4vzoneid), 
                 nl = TRUE)
nlprior <- c(prior(norma(0, 100), nlpar = "bagvpct"))

fit <- brm(formula = model_form, data = dt, 
           family = gaussian(), prior = nlprior)

summary(fit)
marginal_effects(fit)
conditions <- data.frame(hu4vzoneid = unique(dt$hu4vzoneid)[1])
rownames(conditions) <- unique(dt$hu4vzoneid)[1]
me_zone <- marginal_effects(fit, conditions = conditions, 
                            re_formula = NULL, method = "predict")
ran_ef <- as.data.frame(ranef(fit)$hu4vzoneid) %>%
  mutate(zoneid = rownames(.)) %>%
  dplyr::filter(zoneid == unique(dt$hu4vzoneid)[1])

plot(me_zone, ncol = 1)$agvpct + 
  ggtitle(unique(dt$hu4vzoneid)[1]) +
  geom_abline(intercept = 0, slope = 0.6899723 + 1.25)
# ranef slope + fixed slope

ranef(fit)

get_prior(formula = model_form, data = dt)

model_prior <- prior()

fit <- brm(formula = model_form, data = dt, prior = model_prior)

```
